---
title: "Social structure in observed negative movement bias"
output: html_notebook
---

```{r, include=FALSE}
library(reshape2)
library(lme4)
library(sjPlot)
library(effects)
library(MuMIn)
library(qgraph)
library(igraph)
```



1) Visualize the network of influence amoung individuals in the group (influence estimated by Direction Matching)

```{r}
a.s <- read.csv("data/influence_net_obs_neg.csv", header=T,row.names=1)   
m.a<-as.matrix(a.s)

#full
gg<-qgraph((m.a))

```



1) Compare centrality of individuals in the group. Individuals are coded now as Male (M) or Female (F) and a rank score (e.g., top ranking female: F1)

```{r}
gr<-as.igraph(gg)
dat <- data.frame(name=c("M2","F11",  "F2",  "F9",  "F4",	"F10",	"F8",	"F7",	"F6",	"F1",	"M1",	"F5",	"F3"))
dat$rank =              c(2,13,4,11,6,12,10,9,8,3,1,7,5)
dat$InStrength <- strength(gr,mode="in")
dat$OutStrength <- strength(gr,mode="out")
#dat$Betweenness <- betweenness(gr,directed = T, weights=1/E(gr)$weight)
dat$alphaC <- alpha.centrality(gr)
datO <- dat[order(dat$rank),]
dat2<- melt(datO[,-2], id = "name")
positions <- c("M1","M2",  "F1",  "F2",  "F3",	"F4",	"F5",	"F6",	"F7",	"F8",	"F9",	"F10",	"F11")
g <- ggplot(dat2, aes(x = value, y = name, group = variable))+
  geom_point() +
  geom_path() +
  facet_grid(~variable, scales = "free") +
  scale_y_discrete(limits=positions)+theme_bw() + ylab("Individual") + xlab("values")
g
```

3)  Estimate the influence structure of the group using core periphery algorithms

```{r, include=FALSE}
#some functions that we will need

k.core.weighted <- function (graphIn){
  
  coreTest<-data.frame(id<-as.numeric(),ki<-as.numeric())
  colnames(coreTest)<-c("id","ki")
  ids <- c(0,1,2,3,4,5,6,7,8,9,11,12,13)
  
  #calculate ki
  kw <-0
  for (i in 1:13){
    if(i==13){
      coreTest <- rbind(coreTest,c(ids[1],kw))
    }else{
      #print(E(graphIn))
      str.nodes<-strength(graphIn,mode="in")
      str.nodes<-(str.nodes/mean(str.nodes))
      str.nodes<-round(str.nodes+1)#/min(str.nodes))
      d.nodes<-degree(graphIn,mode="in")
      ki <- (d.nodes*str.nodes)^0.5 
      graph.node <- which(ki==min(ki),arr.ind = T)
      minID <- ids[graph.node[1]]
      ids <- ids[-graph.node[1]]
      minK <- ki[graph.node[1]]
      if(is.na(minK)){minK=0} #no connections
      if(is.na(kw)){kw=0} #no connections
      if(kw<minK){kw=minK}
      coreTest <- rbind(coreTest,c(minID,kw))
      if(is.na(graph.node[1])){graph.node[1]=1} #no connections
      graphIn<-delete.vertices(graphIn,graph.node[1])
      #plot(graphIn)
    }
  }
  colnames(coreTest)<-c("id","ki")
  coreTest  
  
}

core.dist <- function(corInd){
  c.d<-0
  for(j in 1:length(corInd)){
    for (k in 1:length(corInd)){
      c.d <- c.d + abs(corInd[j]-corInd[k]) 
    }
  }
  c.d
}

```


```{r}
gg.i<-as.igraph(gg)
rdg.c<-k.core.weighted(gg.i) #function k.core.weighted is at the end of the code
rdg.c<-rdg.c[order(rdg.c$id),]
coreInd.w <- rdg.c[,2]
gg<-qgraph((m.a),groups=factor(coreInd.w),nodeNames=c("Kenny","Alice",  "Alison",  "Catherine",  "Christina",	"Jane",	"Lynn",	"Olga",	"Rushenka",	"Sarah",	"Troy",	"Ulrike",	"Vickie"))

obs.dist<-core.dist(coreInd.w)
```


3.1)  Test the probability that the observed structure could be due to chance (permutation of edges).

```{r}

edeg <- length(E(gg.i))
coreIndex<-data.frame(index<-as.numeric())
coreRand<-data.frame(rn<-as.numeric())

for(i in 1:1000){ #this can be increased (takes a while at 10,000)
  rdg <- sample_gnm(13, edeg, directed = T,loops = F)
  E(rdg)$weight=sample(E(gg.i)$weight) #remove this line to compare non-weighted permutations to the observations
  
  rdg.c <- k.core.weighted(rdg)
  rdg.c <- rdg.c[,2]
  
  coreRand <- rbind(rdg.c,coreRand)
  core.test <-0
  
  for(j in 1:length(rdg.c)){
    for (k in 1:length(rdg.c)){
      core.test <- core.test + abs(rdg.c[j]-rdg.c[k]) 
    }
  }
  coreIndex <- rbind(core.test,coreIndex)
}

#hist(coreIndex[,1])
library(ggplot2)

h.p <- ggplot(coreIndex, aes(coreIndex[,1])) +
  geom_histogram(binwidth = 5,col=I("black"))+
  #geom_freqpoly(binwidth = 5)+
  geom_vline(xintercept = obs.dist,linetype = "longdash")+
  theme_classic()+
  theme(axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
    axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))+
  labs(x=expression(D["core"]), y="Frequency" )
h.p

#Uppler limit of the 95% CI for the random permutations
quantile(coreIndex[,1], 0.95)
```

