---
title: "Movement bias in mobile social troop: baboon group in Dehoop, South Africa"
output: html_notebook
---

```{r, include=FALSE}
library(reshape2)
library(lme4)
library(sjPlot)
library(effects)
library(MuMIn)
library(qgraph)
library(igraph)
library(ggplot2)
library(rethinking)
```


1.)  Visualize the network of influence amoung individuals in the group (influence estimated by Direction Matching): negative and positive influences

```{r}
a.s <- read.csv("data/influence_net_obs.csv", header=T,row.names=1)   
m.a<-as.matrix(a.s)

#full
gg<-qgraph((m.a),nodeNames=c("Kenny","Alice",  "Alison",  "Catherine",  "Christina",	"Jane",	"Lynn",	"Olga",	"Rushenka",	"Sarah",	"Troy",	"Ulrike",	"Vickie"))

```


1.1)  Compare centrality and clustering of individuals in the group. Individuals are coded now as Male (M) or Female (F) and a rank score (Top ranking female: F1)

```{r}
gr<-as.igraph(gg)
dat <- data.frame(name=c("M2","F11",  "F2",  "F9",  "F4",	"F10",	"F8",	"F7",	"F6",	"F1",	"M1",	"F5",	"F3"))
dat$rank =              c(2,13,4,11,6,12,10,9,8,3,1,7,5)
dat$InStrength <- strength(gr,mode="in")
dat$OutStrength <- strength(gr,mode="out")
#dat$Betweenness <- betweenness(gr,directed = T, weights=1/E(gr)$weight)
datO <- dat[order(dat$rank),]
dat2<- melt(datO[,-2], id = "name")
positions <- c("M1","M2",  "F1",  "F2",  "F3",	"F4",	"F5",	"F6",	"F7",	"F8",	"F9",	"F10",	"F11")
g <- ggplot(dat2, aes(x = value, y = name, group = variable))+
  geom_point() +
  geom_path() +
  facet_grid(~variable, scales = "free") +
  scale_y_discrete(limits=positions)+theme_bw() + ylab("Individual") + xlab("values")
g
```

2)  Test the extent to which rank differences can explain influence amoung individuals

```{r}
#get data ready
dy <- read.csv("data/diadic_LMM_sigBay.csv", header=T)   
dy<-subset(dy,dy$delta.rank!=0) #remove giver and recivers that are the same rank (i.e. self loops)
data.sub <- data.frame(influence = dy$att, id = dy$g, rankDiff = dy$delta.rank)

#varying intercept model
m.1 <- map2stan(
  alist (
    influence ~ dnorm(mu, sigma) ,
    mu <- a + a_giver[id] + b*rankDiff,
    a_giver[id] ~ dnorm(0, tau) ,
    a ~ dnorm(0,0.1) ,
    b ~ dnorm(0,0.1) ,
    tau ~ dcauchy(0,0.5) ,
    sigma ~ dcauchy(0, 0.5)
  ),
  data = data.sub, chains = 4, cores = 4, iter = 10000
)

#check model fit
#plot(m.1)
precis(m.1, depth = 2, digits = 4, prob=0.99)
#plot(precis(m.1, depth = 2, digits = 4))
#postcheck(m.1)

#varying intercept-slope model
#m.2 <- map2stan(
#  alist (
#    influence ~ dnorm(mu, sigma) ,
#    mu <- a + a_giver[id] + (b + b_giver[id])*rankDiff ,
#    a ~ dnorm(0,0.1) ,
#    b ~ dnorm(0,0.1) ,
#    c(a_giver,b_giver)[id] ~ dmvnorm2(0, tau, Rho) ,
#    Rho ~ dlkjcorr(2) ,
#    tau ~ dcauchy(0,0.5) ,
#    sigma ~ dcauchy(0, 0.5)
#  ),
#  data = data.sub, chains = 4, cores = 4, iter = 10000
#)#

#compare
#rethinking::compare(m.1,m.2)
#plot(rethinking::compare(m.1,m.2))
```

Examine model predictions
```{r}

rankD.seq <- seq(from = min(data.sub$rankDiff), to = max(data.sub$rankDiff), by = 1)

HPDI.95 <- function(x){
  HPDI(x, prob = 0.95)
}

plot(influence ~ rankDiff , data=data.sub, col=rangi2)
for(i in 1:13){
  if(i!=10){
    data.new <- data.frame(rankDiff =rankD.seq, id=i)
    influence.link <- link(m.1, data.new)
    influence.mean <- apply(influence.link,2,mean)
    influence.HPDI <- apply(influence.link,2,HPDI.95)
    lines(rankD.seq, influence.mean)
    shade(influence.HPDI, rankD.seq)    
  }
}

#post <- extract.samples(m.1)
#dens(post$b)

```

Estimate effect size of the model (at different levels)
```{r}

#generate posterior sampling
postSamples <- 1000
post<-extract.samples(m.1,n=postSamples)

#calculate preditction error at the level of the data point
var.est <- data.frame(var=rep(0,postSamples))
for(i in 1:postSamples){
  data.sub$pred <-  post$a[i] + post$b[i]*data.sub$rankDiff + post$a_giver[i,data.sub$id]
  data.sub$error<- data.sub$influence-data.sub$pred
  var.est[i,1] <- var(data.sub$error)
}

r.square.1 <- 1-mean(var.est[,1])/var(data.sub$influence)
r.square.1 

#calculate prediction error at the level of the intercepts
var.est.obs <- data.frame(var=rep(0,postSamples))
var.est.error <- data.frame(var=rep(0,postSamples))
for(i in 1:postSamples){
  data.sub$obs  <-  post$a_giver[i,data.sub$id]
  data.sub$pred <-  apply(post$a_giver[,data.sub$id],2,mean)
  data.sub$error<-  data.sub$obs-data.sub$pred
  var.est.error[i,1] <-  var(data.sub$error)
  var.est.obs[i,1]   <-  var(data.sub$obs)
}

r.square.2 <- 1-mean(var.est.error[,1])/mean(var.est.obs[,1])
r.square.2 

```
